Unrecognized States: Theory and Cases

### 2022-04-13 teaching.tex
improve argumentation for soln concept

\vskip.3in
\subsection{Timing and Information}
The patron makes its investment. This investment is seen by all other players. Then the home government and secessionists move simultaneously.

\vskip.5in
\subsection{Payoffs}
Let, for instance, ($Status Quo,Rejoin$) mean that $G$ plays $Status Quo$ and $S$ plays $Rejoin$. Then 
\begin{itemize}
	\item The payoffs after ($StatusQuo,StatusQuo$) are $0-p,3,2+p$
		\begin{itemize}
			\item The patron gets neither its favorite or its least favorite outcome. We normalize the patron's payoff from the political outcome to be zero in this case. But the patron pays a cost of whatever amount $p$ it transfers to the secessionists.
			\item Likewise, the government and the secessionists see this outcome as being between their favorite and least favorite (they just have different favorites...). We normalize the status quo to 3 for the government and 2 for the secessionists. However, the secessionists also receive a transfer of $p$ from the patron.
		\end{itemize}
	\item The payoffs after ($StatusQuo,Rejoin$) are $-10-p,5,1$
		\begin{itemize}
			\item The patron's worst outcome is when the secessionists rejoin the home state, so the patron gets a large negative payoff from the political outcome of -10.
			\item The government likes this outcome better than the status quo, so gets 5 instead of 3.
			\item The secessionists dislike this outcome compared to being unrecognized, so get 1 instead of 2.
		\end{itemize}
	\item The payoffs after ($Recognize,StatusQuo$) are $3-p,0,5$
		\begin{itemize}
			\item This is the patron's favorite outcome, but the patron likes this outcome less than it dislikes reunification, so we make the patron's payoff positive but not as large as the magnitude of dislike for reunification of 10.
			\item The government dislikes this outcome compared to having an unrecognized state, so gets 0 instead of 3.
			\item The secessionists like this outcome better than the status quo, so gets 5 instead of 2.
		\end{itemize}
	\item The payoffs after ($Recognize,Rejoin$) are $-p,3,2$
		\begin{itemize}
			\item This is a strange case, because it's not obvious what should happen if both give in at the same time. We assume that, when this happens, nothing changes---that is, we stay in the status quo. But the secessionists don't get the $p$ because they didn't do what the patron wanted them to do.
		\end{itemize}
\end{itemize}

\vskip.5in
\subsection{Solution Concept}
This game has a dynamic component, as the government and the secessionists move after seeing the patron's choice. Further, we assume that the players have symmetric information about payoffs; that is, all the players know the payoffs associated with each outcome. We will also assume that the players know each other well enough to be able to correctly predict each other's behavior; this is likely to be the case when the same leaders have been in place for a while so that they have interacted repeatedly. As this is a high-stakes `game,' all the players have strong incentives to seek out information and think carefully about what the other players will do before choosing the strategy that will maximize their expected payoffs, and this is common knowledge amongst the players. Finally, no commitment devices are available to enforce players' promises, so the players cannot make commitments that are incredible. \\

These assumptions (the game is dynamic, information in symmetric, and the actors have common knowledge of sequential rationality and can correctly predict each other's behavior) imply that Subgame Perfect Nash Equilibrium (SPNE) is the appropriate solution concept for this strategic situation (Watson p. 45 and p. 189).

@@

\subsection{Players and Strategy Spaces}
Same as in Section 1.

\vskip.3in
\subsection{Timing and Information}
Same as in Section 1.

\vskip.5in
\subsection{Payoffs}
\begin{itemize}
	\item The payoffs after ($Status Quo,Status Quo$) are $-p,3,\bm{0}+p$
	\item The payoffs after ($Status Quo,Rejoin$) are $-10-p,5,1$
	\item The payoffs after ($Rejoin,Status Quo$) are $3-p,0,5$
	\item The payoffs after ($Rejoin,Rejoin$) are $-p,3,\bm{0}$
\end{itemize}
The only change(s) from Section 1 is that the secessionist's payoff from ($Status Quo,Status Quo$) has been reduced, and the payoffs from ($Rejoin,Rejoin$) along with it.

\vskip.5in
\subsection{Analysis}
We proceed by backward induction.
\begin{itemize}
	\item In the simultaneous game between $G$ and $S$, $Recognize$ is dominated by $Status Quo$ for player $G$.
		\begin{itemize}
			\item Therefore the Nash Equilibrium (NE) of the subgame is determined by $p$: 
				\begin{itemize}
					\item Again, assume that the secessionists stay in the Status Quo when they're indifferent.
					\item If $0+p \geq 1$ (i.e. $p \geq 1$), the NE is ($Status Quo,Status Quo$).
					\item If $0+p < 1$ (i.e. $p < 1$), the NE is ($Status Quo,Rejoin$).
				\end{itemize}
		\end{itemize}
	\item The Patron's decision: if ($Status Quo,Status Quo$) is the equilibrium in the subgame, the Patron will get a payoff of $-p$. If ($Status Quo,Rejoin$) is the equilibrium in the subgame, the Patron will get a payoff of $-10-p$.
		\begin{itemize}
			\item Since ($Status Quo,Rejoin$) is the worse outcome for the Patron, the patron does not want to invest at all ($p=0$) if ($Status Quo,Rejoin$) is going to be the outcome. 
				\begin{itemize}
					\item In this case, the Patron chooses $p=0$ and the Patron's total payoff is $-10$.
				\end{itemize}
			\item The Patron prefers ($Status Quo,Status Quo$), but to make this happen the Patron must make an investment of $p \geq 1$. Because the Patron's payoff is $-p$, the Patron maximizes its payoffs in this case where it induces ($Status Quo,Status Quo$) by choosing the smallest $p$, which is $p=1$. 
				\begin{itemize}
					\item In this case, the Patron chooses $p=1$ and the Patron's total payoff is $-1$.
				\end{itemize}
			\item Since $-1 > -10$, the Patron will choose to invest $p=1$.
		\end{itemize}
\end{itemize}
Therefore the Subgame Perfect Nash Equilibrium is $p=1$, and ($Status Quo,Status Quo$) as long as $p \geq 1$, ($Status Quo,Rejoin$) if $p < 1$.
\begin{itemize}
	\item $p=1$, ($Status Quo,Status Quo$) is the equilibrium outcome.
\end{itemize}

@@

\vskip.3in
\subsection{Timing and Information}
The patron makes its investment. This investment is seen by all other players. \textbf{Then the international community makes its investment. This investment is seen by all other players.} Then the home government and secessions move simultaneously.

\vskip.5in
\subsection{Payoffs}
We add payoffs for the international community in the second position in the payoff vector since the international community moves second. We also add the international community's investment in the secessionists payoffs from ceding. The international community's payoff from the status quo is normalized to 0. The international community most prefers reunification (the secessionists rejoin, +5) and is strongly opposed to the secessionists being recognized (-7). Here, note that the international community likes its preferred outcome MORE than the patron does, but it dislikes its least preferred outcome LESS than the patron does. This last comparison is crucial for obtaining the outcome we get.
\begin{itemize}
	\item The payoffs after ($Status Quo,Status Quo$) are $-p,\bm{-c},3,0+p$
	\item The payoffs after ($Status Quo,Rejoin$) are $-10-p,\bm{5-c},5,1\bm{+c}$
	\item The payoffs after ($Recognize,Status Quo$) are $3-p,\bm{-7-c},0,5$
	\item The payoffs after ($Recognize,Rejoin$) are $-p,\bm{-c},3,0$
\end{itemize}

>>>>

\subsection{Payoffs}
Let, for instance, ($Status Quo,Rejoin$) mean that $G$ plays $Status Quo$ and $S$ plays $Rejoin$. Then 
\begin{itemize}
	\item The payoffs after ($StatusQuo,StatusQuo$) are $0-p,3,2+p$
		\begin{itemize}
			\item The patron gets neither its favorite or its least favorite outcome. We normalize the patron's payoff from the political outcome to be zero in this case. But the patron pays a cost of whatever amount $p$ it transfers to the secessionists.
			\item Likewise, the government and the secessionists see this outcome as being between their favorite and least favorite (they just have different favorites...). We normalize the status quo to 3 for the government and 2 for the secessionists. However, the secessionists also receive a transfer of $p$ from the patron.
		\end{itemize}
	\item The payoffs after ($StatusQuo,Rejoin$) are $-10-p,5,1$
		\begin{itemize}
			\item The patron's worst outcome is when the secessionists rejoin the home state, so the patron gets a large negative payoff from the political outcome of -10.
			\item The government likes this outcome better than the status quo, so gets 5 instead of 3.
			\item The secessionists dislike this outcome compared to being unrecognized, so get 1 instead of 2.
		\end{itemize}
	\item The payoffs after ($Recognize,StatusQuo$) are $3-p,0,5$
		\begin{itemize}
			\item This is the patron's favorite outcome, but the patron likes this outcome less than it dislikes reunification, so we make the patron's payoff positive but not as large as the magnitude of dislike for reunification of 10.
			\item The government dislikes this outcome compared to having an unrecognized state, so gets 0 instead of 3.
			\item The secessionists like this outcome better than the status quo, so gets 5 instead of 2.
		\end{itemize}
	\item The payoffs after ($Recognize,Rejoin$) are $-p,3,2$
		\begin{itemize}
			\item This is a strange case, because it's not obvious what should happen if both give in at the same time. We assume that, when this happens, nothing changes---that is, we stay in the status quo. But the secessionists don't get the $p$ because they didn't do what the patron wanted them to do.
		\end{itemize}
\end{itemize}

\subsection{Timing and Information}
The patron makes its investment. This investment is seen by all other players. Then the home government and secessionists move simultaneously.\\

We assume all players have complete information about payoffs; that is, all the players know the payoffs associated with each outcome. This assumption could be relaxed if at least one player were difficult for the other players to model (e.g., Vladimir Putin), but in many situations the players will know each other well enough that their information about payoffs will be complete. This is likely to be the case when the same leaders have been in place for a while so that they have interacted repeatedly. We assume the players know each other well for three reasons: (1) it is applicable in many situations; (2) it is simpler; and (3) it serves to highlight the issues on which we are focused. Thus, the only incomplete information in our strategic situation comes from the simultaneous move between the home government and secessionists.

\subsection{Solution Concept}
This game has a dynamic component, as the government and the secessionists move after seeing the patron's choice. Further, in the previous section we argue that the players have complete information about payoffs. Given our assumption that the players know each other well, it is also reasonable to assume that the players will be able to correctly predict each other's behavior. This is particularly true because this is a high-stakes `game,' so all the players have strong incentives to seek out information and think carefully about what the other players will do before choosing the strategy that will maximize their expected payoffs. As this is common knowledge amongst the players and no commitment devices are available to enforce players' promises, the players cannot make either threats or promises that are incredible. \\

These assumptions (the game has an important dynamic component, information about payoffs in complete, and the actors have common knowledge of sequential rationality and can correctly predict each other's behavior) imply that Subgame Perfect Nash Equilibrium (SPNE) is the appropriate solution concept for this strategic situation (Watson p. 45 and p. 189).

@@

\subsection{Players and Strategy Spaces}
Same as in Section 2.

\subsection{Payoffs}
\begin{itemize}
	\item The payoffs after ($Status Quo,Status Quo$) are $-p,3,\bm{0}+p$
	\item The payoffs after ($Status Quo,Rejoin$) are $-10-p,5,1$
	\item The payoffs after ($Rejoin,Status Quo$) are $3-p,0,5$
	\item The payoffs after ($Rejoin,Rejoin$) are $-p,3,\bm{0}$
\end{itemize}
The only change(s) from Section 1 is that the secessionist's payoff from ($Status Quo,Status Quo$) has been reduced, and the payoffs from ($Rejoin,Rejoin$) along with it.

\subsection{Timing and Information}
Same as in Section 2.

\subsection{Solution Concept}
Same as in Section 2.

\vskip.2in
\subsection{Analysis}
We proceed by backward induction.
\begin{itemize}
	\item In the simultaneous game between $G$ and $S$, $Recognize$ is dominated by $Status Quo$ for player $G$.
		\begin{itemize}
			\item Therefore the Nash Equilibrium (NE) of the subgame is determined by $p$: 
				\begin{itemize}
					\item Again, assume that the secessionists stay in the Status Quo when they're indifferent.
					\item If $0+p \geq 1$ (i.e. $p \geq 1$), the NE is ($Status Quo,Status Quo$).
					\item If $0+p < 1$ (i.e. $p < 1$), the NE is ($Status Quo,Rejoin$).
				\end{itemize}
		\end{itemize}
	\item The Patron's decision: if ($Status Quo,Status Quo$) is the equilibrium in the subgame, the Patron will get a payoff of $-p$. If ($Status Quo,Rejoin$) is the equilibrium in the subgame, the Patron will get a payoff of $-10-p$.
		\begin{itemize}
			\item Since ($Status Quo,Rejoin$) is the worse outcome for the Patron, the patron does not want to invest at all ($p=0$) if ($Status Quo,Rejoin$) is going to be the outcome. 
				\begin{itemize}
					\item In this case, the Patron chooses $p=0$ and the Patron's total payoff is $-10$.
				\end{itemize}
			\item The Patron prefers ($Status Quo,Status Quo$), but to make this happen the Patron must make an investment of $p \geq 1$. Because the Patron's payoff is $-p$, the Patron maximizes its payoffs in this case where it induces ($Status Quo,Status Quo$) by choosing the smallest $p$, which is $p=1$. 
				\begin{itemize}
					\item In this case, the Patron chooses $p=1$ and the Patron's total payoff is $-1$.
				\end{itemize}
			\item Since $-1 > -10$, the Patron will choose to invest $p=1$.
		\end{itemize}
\end{itemize}
Therefore the Subgame Perfect Nash Equilibrium is $p=1$, and ($Status Quo,Status Quo$) as long as $p \geq 1$, ($Status Quo,Rejoin$) if $p < 1$.
\begin{itemize}
	\item $p=1$, ($Status Quo,Status Quo$) is the equilibrium outcome.
\end{itemize}

@@

\subsection{Payoffs}
We add payoffs for the international community in the second position in the payoff vector since the international community moves second. We also add the international community's investment in the secessionists payoffs from ceding. The international community's payoff from the status quo is normalized to 0. The international community most prefers reunification (the secessionists rejoin, +5) and is strongly opposed to the secessionists being recognized (-7). Here, note that the international community likes its preferred outcome MORE than the patron does, but it dislikes its least preferred outcome LESS than the patron does. This last comparison is crucial for obtaining the outcome we get.
\begin{itemize}
	\item The payoffs after ($Status Quo,Status Quo$) are $-p,\bm{-c},3,0+p$
	\item The payoffs after ($Status Quo,Rejoin$) are $-10-p,\bm{5-c},5,1\bm{+c}$
	\item The payoffs after ($Recognize,Status Quo$) are $3-p,\bm{-7-c},0,5$
	\item The payoffs after ($Recognize,Rejoin$) are $-p,\bm{-c},3,0$
\end{itemize}

\subsection{Timing and Information}
The patron makes its investment. This investment is seen by all other players. \textbf{Then the international community makes its investment. This investment is seen by all other players.} Then the home government and secessions move simultaneously.

\subsection{Solution Concept}
The addition of the international community does not change any of our assumptions related to the solution concept as long as the international community knows the other three players well and vice versa. Thus we continue to use Subgame Perfect Nash Equilibrium as our solution concept.
